---
title: "Data Preparation"
author: "Yifan Qu, Xi Zou"
output: html_document
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(haven)
library(tidyverse)
```


### Import data

```{r, results='hide', warning=FALSE}
Health_Status_and_Functioning <- read_dta("2015_data/Health_Status_and_Functioning.dta")

Happiness <- Health_Status_and_Functioning %>%
  select(ID,dc042_w3,dc043_w3,dc044_w3,dc028)%>%
  filter(!is.na(dc042_w3),!is.na(dc043_w3),!is.na(dc044_w3),!is.na(dc028))

Demographic_Background <- read_dta("2015_data/Demographic_Background.dta") %>%
  select(ID, ba000_w2_3, ba004_w3_1) %>%
  filter(!is.na(ID), !is.na(ba000_w2_3), !is.na(ba004_w3_1))

Family_transfer <- read_dta("2015_data/Family_Transfer.dta")%>%
  mutate_all(funs(ifelse(is.na(.), 0, .)))

total_support <- Family_transfer$ce009_1_1_ + Family_transfer$ce009_1_2_ + Family_transfer$ce009_1_3_ + Family_transfer$ce009_1_4_ + Family_transfer$ce009_1_5_ + Family_transfer$ce009_1_6_ + Family_transfer$ce009_1_7_ + Family_transfer$ce009_1_8_ + Family_transfer$ce009_1_9_ + Family_transfer$ce009_1_10_ + Family_transfer$ce009_1_11_ + Family_transfer$ce009_1_12_ + Family_transfer$ce009_1_13_ + Family_transfer$ce009_1_14_ + Family_transfer$ce009_1_16_ + Family_transfer$ce009_1_16_
Family_transfer <- cbind(Family_transfer, total_support) %>%
  select(ID, total_support)

Individual_Income <- read_dta("2015_data/Individual_Income.dta") %>%
  select(ID, ga002, hc005,hd001) %>%
  filter(!is.na(ID), !is.na(ga002),!is.na(hc005),!is.na(hd001))

Child <- read_dta("2015_data/Child.dta") %>%
  select(ID, gender, cb069) %>%
  filter(!is.na(ID), !is.na(gender), !is.na(cb069))

Health <- read_dta("2015_data/Health_Status_and_Functioning.dta") %>%
  select(ID, da040, da059, da002_w2_1, da041) %>%
  filter(!is.na(ID), !is.na(da040), !is.na(da059), !is.na(da002_w2_1), !is.na(da041))

```
We import the data set we need from the original data folder, and filter out the factors we need, while removing missing values.

##### Factors:
1. Background information:
Birth year on ID card, gender, children's gender, children's income
2. Health status:
Whether he or she has lost all your teeth, whether to smoke, compared health status with last interview, whether he or she is often troubled with any body pains
3. Financial status:
Income, total family transfer last year, amount of deposit, amount of unpaid loan

### Create the happiness index 

```{r, results='hide', warning=FALSE}
H_4 <- Happiness %>%
  filter(dc043_w3!=6&dc044_w3!=6)%>%
  mutate(index =0.2*dc042_w3 + 0.2* dc043_w3 +0.2*dc044_w3 + 0.4*dc028)
H_3a <- Happiness %>%
  filter(dc043_w3==6)%>%
  mutate(index = 0.3*dc044_w3+0.3*dc042_w3+0.4*dc028)
H_3b <- Happiness %>%
  filter(dc044_w3 == 6)%>%
  mutate(index = 0.3*dc043_w3+0.3*dc042_w3+0.4*dc028)
H_2 <- Happiness%>%
  filter(dc043_w3==6&dc044_w3==6)

hindex<-rbind(H_4,H_3a,H_3b)

```
There are four questions about happiness in the questionnaire, including whether they are satisfied with their health, spouse, children, and overall satisfaction with their lives.
According to the filling outcomes, we have created a weighted happiness index based on the respondents ’answers.

### Merge the datasets

```{r, results='hide', warning= FALSE, message= FALSE}
hindex_v0 <- select(hindex,ID,index)
hindex_v1 <- inner_join(x= hindex_v0,y= Child,by = "ID")
hindex_v2 <- inner_join(x= hindex_v1,y= Demographic_Background,by = "ID")
hindex_v3 <- inner_join(x= hindex_v2,y= Family_transfer,by = "ID")
hindex_v4 <- inner_join(x= hindex_v3,y= Health,by = "ID")
hindex_final <- inner_join(x= hindex_v4,y= Individual_Income,by = "ID")
hindex_final <- hindex_final%>%
  rename(child_gender = gender,child_income = cb069)%>%
  mutate(age = 2015-ba004_w3_1,)

hindex_ml <- hindex_final[,-6]
hindex_ml <- hindex_ml[,-1]

library(Hmisc)
label(hindex_ml$index) <- "happiness index"

```
In the end, we merge all the datasets for machine learning. At the same time, we replace the birth year variable with a new variable(age).
