---
title: "Data Preparation"
author: "Yifan Qu, Xi Zou"
date: "2020/5/5"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(haven)
library(tidyverse)
```


# Data Import
```{r}
Health_Status_and_Functioning <- read_dta("2015_data/Health_Status_and_Functioning.dta")
View(Health_Status_and_Functioning)

Happiness <- Health_Status_and_Functioning %>%
  select(ID,dc042_w3,dc043_w3,dc044_w3,dc028)%>%
  filter(!is.na(dc042_w3),!is.na(dc043_w3),!is.na(dc044_w3),!is.na(dc028))

Demographic_Background <- read_dta("2015_data/Demographic_Background.dta") %>%
  select(ID, ba000_w2_3, ba004_w3_1) %>%
  filter(!is.na(ID), !is.na(ba000_w2_3), !is.na(ba004_w3_1))

Family_transfer <- read_dta("2015_data/Family_Transfer.dta")%>%
  mutate_all(funs(ifelse(is.na(.), 0, .)))
total_support <- Family_transfer$ce009_1_1_ + Family_transfer$ce009_1_2_ + Family_transfer$ce009_1_3_ + Family_transfer$ce009_1_4_ + Family_transfer$ce009_1_5_ + Family_transfer$ce009_1_6_ + Family_transfer$ce009_1_7_ + Family_transfer$ce009_1_8_ + Family_transfer$ce009_1_9_ + Family_transfer$ce009_1_10_ + Family_transfer$ce009_1_11_ + Family_transfer$ce009_1_12_ + Family_transfer$ce009_1_13_ + Family_transfer$ce009_1_14_ + Family_transfer$ce009_1_16_ + Family_transfer$ce009_1_16_
Family_transfer <- cbind(Family_transfer, total_support) %>%
  select(ID, total_support)

Individual_Income <- read_dta("2015_data/Individual_Income.dta") %>%
  select(ID, ga002, hc005,hd001) %>%
  filter(!is.na(ID), !is.na(ga002),!is.na(hc005),!is.na(hd001))

Child <- read_dta("2015_data/Child.dta") %>%
  select(ID, gender, cb069) %>%
  filter(!is.na(ID), !is.na(gender), !is.na(cb069))

Health <- read_dta("2015_data/Health_Status_and_Functioning.dta") %>%
  select(ID, da040, da059, da002_w2_1, da041) %>%
  filter(!is.na(ID), !is.na(da040), !is.na(da059), !is.na(da002_w2_1), !is.na(da041))

```
We import the data set we need from the original data folder, and filter out the factors we need, while removing missing values.

### Factors:
1. Background information:
Income, gender, children's gender, children's income, family transfer in 2015
2. Health status:
Whether he or she has lost all your teeth, whether to smoke, compared health status with last interview, whether he or she is often troubled with any body pains
3.
